How young children integrate information during word learning

### 2020-05-17 paper/bda_fig.tex
modify bda figure
update supplement! !

\begin{figure}[ht]
\begin{center}
\begin{tabular}{cc}
\begin{tikzpicture}
%% RSA nodes and data
\node[obs](data_comb){$d^{CM}_{ijk}$};
\node[obs, xshift=-3cm, yshift=0cm](data_me){$d^{ME}_{ij}$};
\node[obs, xshift=3cm,  yshift=0cm](data_cg){$d^{CG}_{i}$};

\node[det, above=of data_me](L1_me){$L'_{ij}$};
\node[det, above=of data_comb](L1_comb){$L_{ijk}$};
\node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};

@@

\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (8,0) {Integration model\\ $P_{L}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) $\\ 
$P_{S}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P(r \mid u; \{\theta_{ij}\}) ^{\alpha_i} $\\
$P(r \mid u; \{\theta_{ij}\}) \propto \mathcal{L}(u, r \mid \theta_{ij})$
};

>>>>

\begin{figure}[ht]
\begin{center}
\begin{tabular}{cc}

\begin{tikzpicture}
%% RSA nodes and data
\node[obs](data_comb){$d^{CM}_{ijk}$};
\node[obs, xshift=-3cm, yshift=0cm](data_me){$d^{ME}_{ij}$};
\node[obs, xshift=3cm,  yshift=0cm](data_cg){$d^{CG}_{i}$};

\node[det, above=of data_me](L1_me){$L'_{1_{ij}}$};
\node[det, above=of data_comb](L1_comb){$L_{1_{ij}}$};
\node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};

@@

\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (8,0) {Integration model\\ $P_{L_{1}}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) $\\ 
$P_{S}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P(r \mid u; \{\theta_{ij}\}) ^{\alpha_i} $\\
$P(r \mid u; \{\theta_{ij}\}) \propto \mathcal{L}(u, r \mid \theta_{ij})$
};

### 2020-05-17 paper/supplementary_material.Rmd
update supplement! !

---
title: "Word learning at the semantics pragmatics interface"
subtitle: "Supplementary material"
author: "Manuel Bohn, Michael Henry Tessler, Megan Merrick and Michael C. Frank"
output: 
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
  bookdown::pdf_document2:
    toc: yes 
    number_sections: false    
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\thetable}{S\arabic{table}} 
  \renewcommand{\thefigure}{S\arabic{figure}}
---

>>>>

---
title: "How young children integrate information during word learning"
subtitle: "Supplementary material"
author: "Manuel Bohn, Michael Henry Tessler, Megan Merrick and Michael C. Frank"
output: 
  bookdown::pdf_document2:
    toc: yes 
    number_sections: false    
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\thetable}{S\arabic{table}} 
  \renewcommand{\thefigure}{S\arabic{figure}}
---
